The relative roles of genetic, ecological and environmental factors in species radiations

### 2018-02-20 paper/draft.tex
fix
fix equation
add ref against protracted spec. to intro

Recently, a group of influential island biogeography researchers proposed a set of 50 questions in island biogeography that still need answering (Patiño et al. 2017).
A subset of these questions deals with the topic of speciation and radiations on islands.
%% Yet, there are numerous examples for fascinating patterns of trait distributions and evolution on islands, such as island syndromes[, ...] or the fact of explosively radiating lineages (Hughes \& Eastwood 2006, Kocher 2004)
%%, while others remain one single species (Price/Chase) (eg. \cite{price2004speciation}).

@@

In a recent review \cite{leidinger2017biodiversity}, we analyzed a powerful alternative to field experiments in island biogeography: mechanistic (/simulation) models.
Although many of the reviewed models integrate multiple processes at a time, unfortunately, most models failed to include more explicit genetic or micro evolution processes.
Instead, some models used concepts such as ``protracted speciaton'' \cite{rosindellXXX},
where speciation occurs with a delay from the actual
divergence event if the population remains isolated during that time.
But nature is usually more complex than this and genetic mechanisms have important ramifications for speciation/radiation and species richness.

@@

Building on the model of Cabral et al. (2017a, b), most of the biological rates are controlled following the metabolic theory
of ecology (MTE, Brown et al.\ 2004).
In MTE, a biological rate $b$ depends on the temperature $T$ and individual mass $M$, scaling a base rate $b_0$ as:
\begin{equation}
  $b=b_0*M^{3/4}*exp(-E_A/{k_B*T})$
  \label{eq:MTE}
\end{equation}
with $E_A$ the activation energy and $k_B$ the Boltzman constant.

>>>>

Recently, a group of influential island biogeography researchers proposed a set of 50 questions in island biogeography that still need answering (Patiño et al.\ 2017).
A subset of these questions deals with the topic of speciation and radiations on islands.
%% Yet, there are numerous examples for fascinating patterns of trait distributions and evolution on islands, such as island syndromes[, ...] or the fact of explosively radiating lineages (Hughes \& Eastwood 2006, Kocher 2004)
%%, while others remain one single species (Price/Chase) (eg. \cite{price2004speciation}).

@@

In a recent review \cite{leidinger2017biodiversity}, we analyzed a powerful alternative to field experiments in island biogeography: mechanistic (/simulation) models.
Although many of the reviewed models integrate multiple processes at a time, unfortunately, most models failed to include more explicit genetic or micro evolution processes.
Instead, some models used concepts such as ``protracted speciaton'' \cite{rosindellXXX},
where speciation occurs with a delay from the actual
divergence event if the population remains isolated during that time.
But nature is usually more complex than this (cf.\ Herben et al.\ 2005) and genetic mechanisms can have important ramifications for speciation/radiation and species richness.

@@

Building on the model of Cabral et al. (2017a, b), most of the biological rates are controlled following the metabolic theory
of ecology (MTE, Brown et al.\ 2004).
In MTE, a biological rate $b$ depends on the temperature $T$ and individual mass $M$, scaling a base rate $b_0$ as:
\begin{equation}
  b=b_0*M^{3\over4}*e^{-{E_A}\over{k_B*T}}
  \label{eq:MTE}
\end{equation}
with $E_A$ the activation energy and $k_B$ the Boltzman constant.
